Results_paper1

### 2019-04-17 Paper1_results.Rmd
updated

library(tidyverse)
library(plyr)
library(lubridate)
library(ggpubr)
library(zoo)
library(lubridate)
library(FNN)
library(forecast)
library(astrochron)
library(WaveletComp)
library(data.table)
library(heatwaveR)
library(viridis)
library(ggrepel)
library(plyr)
library(maptools)
library(sp)
library(geosphere)
library(marmap)
library(PBSmapping)
library(scales)
library(grid)
library(gridExtra)
library(circular)
library(fossil)
library(mapproj)
library(rgeos)
library(ncdf4)
# library(sinkr)
library(spacetime)
library(reshape2)
library(plyr) # Never load plyr when also loading the tidyverse. It causes a lot of conflicts.
library(stringr)
library(doMC); doMC::registerDoMC(cores = 4)
library(fasttime)

@@

# Remotely sensed SST datasets
Matching the satellite sea surface temperature data point to the in situ temperature collected data points.

@@

```{r}
MUR_Lamberts_Bay <- read_csv("Data/MUR_nearest5pixels/MUR_Lamberts Bay_SST_timeseries_5nearest.csv")
MUR_Port_Nolloth <- read_csv("Data/MUR_nearest5pixels/MUR_Port Nolloth_SST_timeseries_5nearest.csv")
MUR_Saldanha_Bay <- read_csv("Data/MUR_nearest5pixels/MUR_Saldanha Bay_SST_timeseries_5nearest.csv")
MUR_Yzerfontein <- read_csv("Data/MUR_nearest5pixels/MUR_Yzerfontein_SST_timeseries_5nearest.csv")
MUR_Kommetjie <- read_csv("Data/MUR_nearest5pixels/MUR_Kommetjie_SST_timeseries_5nearest.csv")
MUR_Sea_Point <- read_csv("Data/MUR_nearest5pixels/MUR_Sea Point_SST_timeseries_5nearest.csv")

@@

MUR_plot <- match_plot(df = insitu_MUR)
MUR_plot <- temp_plot(df = insitu_MUR)
```

@@

```{r}
Lamberts_Bay <- read_csv("Data/G1SST_sub/Lamberts Bay_SST_timeseries_5nearest.csv")
Port_Nolloth <- read_csv("Data/G1SST_sub/Port Nolloth_SST_timeseries_5nearest.csv")
Saldanha_Bay <- read_csv("Data/G1SST_sub/Saldanha Bay_SST_timeseries_5nearest.csv")
Yzerfontein <- read_csv("Data/G1SST_sub/Yzerfontein_SST_timeseries_5nearest.csv")
Kommetjie_SST <- read_csv("Data/G1SST_sub/Kommetjie_SST_timeseries_5nearest.csv")
Sea_Point_SST<- read_csv("Data/G1SST_sub/Sea Point_SST_timeseries_5nearest.csv")

@@

G1SST_plot <- match_plot(df = insitu_G1SST )
G1SST_temp_plot <- temp_plot(df = insitu_G1SST)
```

@@

```{r}
Lamberts_Bay <- read_csv("Data/K10/K10_Lamberts Bay_SST_timeseries_5nearest.csv")
Port_Nolloth <- read_csv("Data/K10/K10_Port Nolloth_SST_timeseries_5nearest.csv")
Saldanha_Bay <- read_csv("Data/K10/K10_Saldanha Bay_SST_timeseries_5nearest.csv")
Yzerfontein <- read_csv("Data/K10/K10_Yzerfontein_SST_timeseries_5nearest.csv")
Kommetjie <- read_csv("Data/K10/K10_Kommetjie_SST_timeseries_5nearest.csv")
Sea_Point <- read_csv("Data/K10/K10_Sea Point_SST_timeseries_5nearest.csv")

@@

K10_plot <- match_plot(df = insitu_K10)
k10_temp_plot <- temp_plot(df = insitu_K10)
```

@@

OISST_plot <- match_plot(df = insitu_OISST)
OISST_temp_plot <- temp_plot(df = insitu_OISST)
```

@@

The aim of this is to find the temperature collected at different distances from the coast (distances = 15km, 25km, 35km and 50km). Then create wavelet analyses (or another analyses) where I compare how the intensity and duration of upwelling vary at different distances from the coastline. So would I have a dataset with temperature at 15km then at 25km then at 50km and so on...?

@@

# Manually correcting Sea Point and Kommetjie
site_transects$heading[5:6] <- 290 
save(site_transects, file = "Data_P1/site_transects.RData")
load("Data_P1/site_transects.RData")

@@

# Pixel points
site_pixels <- data.frame()
for(i in 1:length(west$site)){
  site <- site_transects[i,]
  site_pixel <- transect.pixel(site, c(15000, 25000, 35000, 45000, 55000)) # RWS: The desired distances
  site_pixels <- rbind(site_pixels, site_pixel)
}

@@

# Bounding box
  # Only one is made in order to know how large the the geom_point() squares should be made to match
test <- data.frame(xmin = destPoint(p = site_pixels[1,2:3], b = 270, d = 12500)[1],
                   xmax = destPoint(p = site_pixels[1,2:3], b = 90, d = 12500)[1],
                   ymin = destPoint(p = site_pixels[1,2:3], b = 180, d = 12500)[2],
                   ymax = destPoint(p = site_pixels[1,2:3], b = 0, d = 12500)[2])
```

@@

load("Data_P1/south_africa_coast.RData")
load("Data_P1/bathy/sa_bathy.RData")
names(south_africa_coast)[1] <- "lon"

@@

# Plotting with pixel boxes
plot1 <- ggplot() +
 geom_contour(data = bathy[bathy$depth >= -250,], aes(x = lon, y = lat, z = depth),
               colour = "grey20", alpha = 0.7, size = 0.2, binwidth = 200, na.rm = TRUE, show.legend = FALSE) +
  stat_contour(data = sa_bathy[sa_bathy$depth < -250,], aes(x = lon, y = lat, z = depth, alpha = ..level..),
               colour = "grey20", size = 0.1, binwidth = 1000, na.rm = TRUE, show.legend = FALSE) +
  geom_polygon(data = south_africa_coast, aes(x = lon, y = lat, group = group), 
               size = 0.5, colour = "black", fill = "white") +
   # geom_text(data = west, aes(x = lon, y = lat, label = site),
   #          size = 1.8, colour = "black") +
  # geom_polygon(data = wcBox, aes(x = lon, y = lat, group = group), alpha = 0.20, 
  #              colour = "bisque1", fill = "bisque1") +
  geom_point(data = west, aes(x = lon, y = lat), alpha = 0.8, size = 1.6) +
  geom_text(data = west, aes(x = lon, y = lat, label = site), 
                     size = 6, box.padding = 2, nudge_x = -0.5, nudge_y = 0.2, 
                     segment.alpha = 0.4, force = 0.1) +
  geom_point(data = site_pixels, aes(x = lon, y = lat), colour = "black", shape = 0, alpha = 0.8, size = 2.1) +
  scale_alpha_continuous(breaks = c(-200, -1000, -2000, -3000, -4000, -5000),
                         guide_legend(title = "depth (m)")) +
  scale_fill_gradient(low = "dodgerblue4", high = "dodgerblue", na.value = "steelblue4", 
                      breaks = c(-1000, -2000, -3000, -4000, -5000),
                      guide_legend(title = "depth (m)")) +
   annotate("text", label = "INDIAN\nOCEAN", x = 34.00, y = -35.0,
             size = 6.0, angle = 0, colour = "black") +
    annotate("text", label = "ATLANTIC\nOCEAN", x = 14.00, y = -35.0,
             size = 6.0, angle = 0, colour = "black") +
    annotate("text", label = "Benguela", x = 15.0, y = -31.7,
             size = 4.0, angle = 302, colour = "black") +
    annotate("text", label = "Agulhas", x = 32.0, y = -31.7,
             size = 4.0, angle = 50, colour = "black") +
  labs(title = NULL, x = NULL, y = NULL) +
  theme(legend.key = element_rect(colour = NA, size = 0.2),
        legend.key.height = unit(0.4, "cm"),
        legend.background = element_blank()) +
  coord_cartesian(xlim = sa_lons, ylim = sa_lats) 
plot1
```

@@

renaming_sites_1 <- function(df) {
  sites <- df %>%
      # RWS: An alternative way to replace values without having to use multiple ifelse() statements
      mutate(temp_sites = case_when(station_name == "CAPE COLUMBINE" ~ "St Helena Bay",
                                    station_name  == "KOINGNAAS" ~ "Hondeklipbaai",
                                    station_name  == "PORT NOLLOTH" ~"Port Nolloth",
                                    station_name  == "LAMBERTSBAAI NORTIER" ~ "Lamberts Bay",
                                    station_name  == "LANGEBAANWEG AWS" ~ "Saldanha Bay"))
  return(sites)
}

wind_sitesmatched_1 <-  renaming_sites_1(df = wind_1)
# RWS: You should never be removing values by specific call like this
  # Rather you should be able to use some sort of conditional to screen out unwanted values
wind_sitesmatched_1 <- wind_sitesmatched_1[-c(121352, 121353, 379892, 379893, 609324, 609325, 843506, 843507, 1014585), ]

renaming_sites_2 <- function(df) {
  sites <- df %>%
    mutate(temp_sites = ifelse(station_name %in% c("ROBBENEILAND"), "Koeberg Basin",        
                           ifelse(station_name %in% c("GEELBEK"), "Yzerfontein",
                                ifelse(station_name %in% c("DASSEN ISLAND"), "Dassen Island",
                                       ifelse(station_name %in% c("ATLANTIS"), "Koeberg Basin","Error")))))
  return(sites)
}

wind_sitesmatched_2 <-  renaming_sites_2(df = wind_2)
wind_sitesmatched_2 <- wind_sitesmatched_2[-c(228372, 228373, 313441, 313442, 364881, 364882, 557392), ]

renaming_sites_3 <- function(df) {
  sites <- df %>%
    mutate(temp_sites = ifelse(station_name %in% c("CAPE TOWN SLANGKOP"), "Kommetjie",  
                           ifelse(station_name %in% c("CAPE TOWN - ROYAL YACHT CLUB"), "Sea Point",
                           ifelse(station_name %in% c("CAPE TOWN TABLE BAY"), "Sea Point","Error"))))
  return(sites)
}

wind_sitesmatched_3 <-  renaming_sites_3(df = wind_3)
wind_sitesmatched_3 <- wind_sitesmatched_3[-c(119317, 119318, 196551, 196552, 346759), ]

## CAPE TOWN SLANGKOP may be used for Kommetjie and for Houtbay
wind_3_HoutBay <- wind_3 %>% 
  filter(station_name == "CAPE TOWN SLANGKOP") %>% 
  mutate(temp_sites = ifelse(station_name %in% c("CAPE TOWN SLANGKOP"), "Hout Bay","Error"))

wind_data <- rbind(wind_3_HoutBay,wind_sitesmatched_3,wind_sitesmatched_2,wind_sitesmatched_1)
wind_data <- wind_data %>% 
  na.omit()

wind_data <- wind_data %>% 
  # mutate(date = as.Date(date)) %>%  
  group_by(date, hour, temp_sites)

# write.csv(wind_data, file = "Data_P1/wind_data.csv", row.names = T)
# save(wind_data, file = "Data_P1/wind_data.RData")

@@

# wind_data <- read_csv("Data_P1/wind_data.csv")

wind_daily <- wind_data %>%
  # ungroup() %>%
  # mutate(date = as.Date(date))%>%
  dplyr::group_by(temp_sites, date) %>%
  dplyr::summarise(dir_circ = round(mean.circular(circular(dir, units = "degrees")),2),
                   mean_speed = round(mean(speed),2))

# save(wind_daily, file = "Data_P1/wind_daily.RData")
# Loading in the daily wind data
load("Data_P1/wind_daily.RData")

# Subsetting to particular sites 
selected_sites <- c("Port Nolloth", "Lamberts Bay", "Sea Point", "Saldanha Bay", "Yzerfontein", "Kommetjie")

wind_daily_sub <- wind_daily %>% 
  dplyr::rename(site = temp_sites) %>% 
  filter(site %in% selected_sites)

# save(wind_daily_sub, file = "Data_P1/wind_daily_sub.RData")
# Loading in the daily wind data
# load("Data_P1/wind_daily_sub.RData")
```

@@

```{r}
insitu_wind <- match_func(df = wind_daily_sub) %>%
  drop_na()
insitu_wind <- insitu_wind %>% 
  filter(year(date) %in% seq(2010, 2014)) # The years 2010-2014 is the years of interest and the years for which wavelets are/will be created.

# save(insitu_wind, file = "Data_P1/insitu_wind.RData")
# Loading in the daily wind data
# load("Data_P1/insitu_wind.RData")
```

@@

```{r}
wave_daily_renamed <- insitu_wind %>% 
  dplyr::rename(spd = mean_speed) %>%
  dplyr::rename(dir = dir_circ)

p.wr2 <- plot.windrose(data = wave_daily_renamed,
              spd = "spd",
              dir = "dir")
p.wr3 <- p.wr2 + facet_wrap(.~ site, ncol = 2, nrow = "") +
  theme(strip.text.x = element_text(size = 25))
p.wr3 # RWS: You'll want to remove the NA part in the figure output
```

@@

region <- "BC" # Benguela Current
# coords <- bbox[, region] # RWS: Where does bbox come from?
coords <- c(-35, -20, 10, 20) # this is the BC

ncList <- list.files(path = MODIS_chlor.dir, pattern = "*.nc", full.names = TRUE, include.dirs = TRUE)
strt.date <- str_sub(basename(ncList[1]), start = 2, end = 8)
end.date <- str_sub(basename(ncList[length(ncList)]), start = 2, end = 8)
nc.init <- nc_open(ncList[1])
LatIdx <- which(nc.init$dim$lat$vals > coords[1] & nc.init$dim$lat$vals < coords[2])
LonIdx <- which(nc.init$dim$lon$vals > coords[3] & nc.init$dim$lon$vals < coords[4])
nc_close(nc.init)

ncFun <- function(nc.file = nc.files, csv.dir = csv.dir) {
nc <- nc_open(nc.file)
  instrument <- ncatt_get(nc, 0, "instrument")$value
  platform <- ncatt_get(nc, 0, "platform")$value
  product_name <- ncatt_get(nc, 0, "product_name")$value
  fNameStem <- substr(product_name, 17, 38)
  timeStamp <- substr(product_name, 2, 8)
  origin <- paste0(substr(timeStamp, 1, 4), "-01-01")
  date <- as.Date(as.numeric(substr(timeStamp, 5, 7)), origin)
  chl <- round(ncvar_get(nc,
                   varid = "chlor_a",
                   start = c(LonIdx[1], LatIdx[1]),
                   count = c(length(LonIdx), length(LatIdx))),
               3)
  dimnames(chl) <- list(lon = nc$dim$lon$vals[LonIdx],
                        lat =  nc$dim$lat$vals[LatIdx])
  nc_close(nc)
  chl <-
    as.data.table(melt(chl, value.name = "chl"), row.names = NULL) %>%
    mutate(t = date) %>%
    na.omit()
  fwrite(chl,
         file = paste(csv.dir, "/", region, "-", instrument, ".",platform, ".",
                      fNameStem, "-", strt.date, "-", end.date, ".csv", sep = ""),
         append = TRUE, col.names = FALSE)
  rm(chl)
}

llply(ncList, ncFun, csv.dir = MODIS_chlor.csv.dir, .parallel = TRUE)

@@

# Loading the data
load("Data_P1/MODIS_Chloro.RData") # Extracted/Raw chlorophyll data
load("Data_P1/site_list_sub.Rdata") # Site list of all the sites along the west coast

# Visualisation
chloro_plot <- MODIS_Chloro %>%
  filter(date == min(date)) %>%
  ggplot(aes(x = lon, y = lat)) +
  geom_raster(aes(fill = chloro))

unique_pixel <- MODIS_Chloro %>% 
  select(lon, lat) %>% 
  unique()

match_index <- knnx.index(data = as.matrix(unique_pixel[,1:2]),
                          query = as.matrix(site_list_sub[,5:6]), k = 1)

# Matching the chlorophylla-a lats and lons to the study sites
pixel_match <- unique_pixel[match_index,] %>%
  unite(col = combi, lon, lat, sep = "/", remove = F) %>%
  mutate(site = site_list_sub$site)

chloro_match <- MODIS_Chloro %>%
  unite(col = combi, lon, lat, sep = "/", remove = F) %>%
  filter(combi %in% pixel_match$combi)

chloro_match %>%
  filter(date == max(date)) %>%
  ggplot(aes(x = lon, y = lat)) +
  geom_raster(aes(fill = chloro))

chloro_sites <- chloro_match %>%
  left_join(pixel_match, by = c("combi", "lon", "lat")) %>% 
  dplyr::mutate(date = as.Date(date))
# save(chloro_sites, file = "Data_P1/chloro_sites.RData")

# Visualisation
Chloro_plot_complete <- ggplot(chloro_sites, aes(x = date, y = chloro)) +
  geom_line() +
  facet_wrap(~site, ncol = 1)
Chloro_plot_complete

# Study period from 2010 - 2014
chloro_data <- chloro_sites %>% 
  filter(year(date) %in% seq(2010, 2014))
# save(chloro_data, file = "Data_P1/chloro_data.RData")

# Plotting only years 2014-2015
Chloro_plot_filtered <- ggplot(chloro_data, aes(x = date, y = chloro)) +
  geom_line() +
  facet_wrap(~site, ncol = 1)
Chloro_plot_filtered

@@

>>>>

library(tidyverse)
library(plyr)
library(lubridate)
library(ggpubr)
library(zoo)
library(lubridate)
library(FNN)
library(forecast)
library(astrochron)
library(WaveletComp)
library(data.table)
library(heatwaveR)
library(viridis)
library(ggrepel)
library(plyr)
library(maptools)
library(sp)
library(geosphere)
# library(marmap)
library(PBSmapping)
library(scales)
library(grid)
library(gridExtra)
library(circular)
library(fossil)
library(mapproj)
# library(rgeos)
library(ncdf4)
# library(sinkr)
library(spacetime)
library(reshape2)
library(plyr) # Never load plyr when also loading the tidyverse. It causes a lot of conflicts.
library(stringr)
library(doMC); doMC::registerDoMC(cores = 4)
library(fasttime)

@@

# Remotely sensed SST datasets
Matching the satellite sea surface temperature data point to the in situ temperature collected data points. The MUR data is not present within the data_P1 folder and so needs to be loaded into the data folder.

@@

```{r}
MUR_Lamberts_Bay <- read_csv("Data_P1/MUR_nearest5pixels/MUR_Lamberts Bay_SST_timeseries_5nearest.csv")
MUR_Port_Nolloth <- read_csv("Data_P1/MUR_nearest5pixels/MUR_Port Nolloth_SST_timeseries_5nearest.csv")
MUR_Saldanha_Bay <- read_csv("Data_P1/MUR_nearest5pixels/MUR_Saldanha Bay_SST_timeseries_5nearest.csv")
MUR_Yzerfontein <- read_csv("Data_P1/MUR_nearest5pixels/MUR_Yzerfontein_SST_timeseries_5nearest.csv")
MUR_Kommetjie <- read_csv("Data_P1/MUR_nearest5pixels/MUR_Kommetjie_SST_timeseries_5nearest.csv")
MUR_Sea_Point <- read_csv("Data_P1/MUR_nearest5pixels/MUR_Sea Point_SST_timeseries_5nearest.csv")

@@

MUR_plot <- match_plot(df = insitu_MUR)
MUR_temp <- temp_plot(df = insitu_MUR)
```

@@

```{r}
Lamberts_Bay <- read_csv("Data_P1/G1SST_sub/Lamberts Bay_SST_timeseries_5nearest.csv")
Port_Nolloth <- read_csv("Data_P1/G1SST_sub/Port Nolloth_SST_timeseries_5nearest.csv")
Saldanha_Bay <- read_csv("Data_P1/G1SST_sub/Saldanha Bay_SST_timeseries_5nearest.csv")
Yzerfontein <- read_csv("Data_P1/G1SST_sub/Yzerfontein_SST_timeseries_5nearest.csv")
Kommetjie_SST <- read_csv("Data_P1/G1SST_sub/Kommetjie_SST_timeseries_5nearest.csv")
Sea_Point_SST<- read_csv("Data_P1/G1SST_sub/Sea Point_SST_timeseries_5nearest.csv")

@@

G1SST_plot <- match_plot(df = insitu_G1SST )
G1SST_temp<- temp_plot(df = insitu_G1SST)
```

@@

```{r}
Lamberts_Bay <- read_csv("Data_P1/K10/K10_Lamberts Bay_SST_timeseries_5nearest.csv")
Port_Nolloth <- read_csv("Data_P1/K10/K10_Port Nolloth_SST_timeseries_5nearest.csv")
Saldanha_Bay <- read_csv("Data_P1/K10/K10_Saldanha Bay_SST_timeseries_5nearest.csv")
Yzerfontein <- read_csv("Data_P1/K10/K10_Yzerfontein_SST_timeseries_5nearest.csv")
Kommetjie <- read_csv("Data_P1/K10/K10_Kommetjie_SST_timeseries_5nearest.csv")
Sea_Point <- read_csv("Data_P1/K10/K10_Sea Point_SST_timeseries_5nearest.csv")

@@

K10_plot <- match_plot(df = insitu_K10)
k10_temp <- temp_plot(df = insitu_K10)
```

@@

OISST_plot <- match_plot(df = insitu_OISST)
OISST_temp <- temp_plot(df = insitu_OISST)
```

@@

The aim of this is to find the temperature collected at different distances from the coast (distances = 15km, 25km, 35km and 50km).

@@

# Manually correcting Sea Point and Kommetjie
site_transects$heading[5:6] <- 290 
# save(site_transects, file = "Data_P1/site_transects.RData")
load("Data_P1/site_transects.RData")

@@

# Pixel points
site_pixels <- data.frame()
for(i in 1:length(west$site)){
  site <- site_transects[i,]
  site_pixel <- transect.pixel(site, c(10000, 20000, 30000, 40000, 50000)) # RWS: The desired distances
  site_pixels <- rbind(site_pixels, site_pixel)
}

@@

# Bounding box
  # Only one is made in order to know how large the the geom_point() squares should be made to match
bbox <- data.frame(xmin = destPoint(p = site_pixels[1,2:3], b = 270, d = 12500)[1],
                   xmax = destPoint(p = site_pixels[1,2:3], b = 90, d = 12500)[1],
                   ymin = destPoint(p = site_pixels[1,2:3], b = 180, d = 12500)[2],
                   ymax = destPoint(p = site_pixels[1,2:3], b = 0, d = 12500)[2])

# Determining the temperature at the various distances from the coast
```

@@

load("Data_P1/south_africa_coast.RData")
load("Data_P1/bathy/sa_bathy.RData")
load("Data_P1/bathy/bathy.RData")
names(south_africa_coast)[1] <- "lon"

@@

 plot1 <- ggplot() +#coord_equal() + 
  geom_raster(data = sa_bathy, aes(x = lon, y = lat, fill = depth)) +
  #geom_raster(data = isobath200, aes(x = lon, y = lat, fill = coast)) +
  stat_contour(data = sa_bathy, aes(x = lon, y = lat, z = depth, alpha = ..level..), 
               colour = "black", size = 0.2, binwidth = 200, na.rm = TRUE, show_guide = FALSE) +
  geom_polygon(data = south_africa_coast, aes(x = lon, y = lat, group = group), 
               size = 0.5, colour = "black", fill = "white") +
  #geom_path(data = sa_provinces_new, aes(x = long, y = lat, group = group)) +
  # geom_polygon(data = wcBox, aes(x = lon, y = lat, group = group), alpha = 0.20, 
  #              colour = "bisque1", fill = "bisque1") +
  geom_point(data = site_list_sub, aes(x = lon, y = lat), alpha = 0.8, size = 1.6) +
  geom_point(data = site_pixels, aes(x = lon, y = lat), colour = "white", shape = 0, alpha = 0.8, size = 2.1) +
  geom_rect(data = bbox, aes(xmin = xmin, xmax = xmax, ymin = ymin, ymax = ymax), 
            alpha = 0.4, colour = "red", size = 0.1, linetype = 1) +
  scale_alpha_continuous(breaks = c(-200, -1000, -2000, -3000, -4000, -5000),
                         guide_legend(title = "depth (m)")) +
  scale_fill_gradient(low = "dodgerblue4", high = "dodgerblue", na.value = "steelblue4", 
                      breaks = c(-1000, -2000, -3000, -4000, -5000),
                      guide_legend(title = "depth (m)")) +
  labs(title = NULL, x = NULL, y = NULL) +
  guides(colour = guide_legend(override.aes = list(size = 3))) +
  #guide_legend(ncol = 2) +
  theme(legend.key = element_rect(colour = NA, size = 0.2),
        legend.key.height = unit(0.4, "cm"),
        legend.background = element_blank()) +
        #legend.justification = c(1,0), legend.position = c(0.5, 0.4)) +
  coord_cartesian(xlim = sa_lons, ylim = sa_lats)
 plot1

 # Added in the bathy data but this is not needed for any of the analyses.
 # This just shows the bounding boxes 
```

@@

renaming_sites_1 <- function(df) {
  sites <- df %>%
      # RWS: An alternative way to replace values without having to use multiple ifelse() statements
      mutate(temp_sites = case_when(station_name == "CAPE TOWN TABLE BAY" ~ "Sea Point",
                                    station_name == "CAPE TOWN - ROYAL YACHT CLUB" ~ "Sea Point",
                                    station_name  == "GEELBEK" ~ "Yzerfontein",
                                    station_name  == "CAPE TOWN SLANGKOP" ~ "Kommetjie",
                                    station_name  == "PORT NOLLOTH" ~"Port Nolloth",
                                    station_name  == "LAMBERTSBAAI NORTIER" ~ "Lamberts Bay",
                                    station_name  == "LANGEBAANWEG AWS" ~ "Saldanha Bay"))
  return(sites)
}

wind_sitesmatched_1 <-  renaming_sites_1(df = wind_1)
wind_sitesmatched_2 <-  renaming_sites_1(df = wind_2)
wind_sitesmatched_3 <-  renaming_sites_1(df = wind_3)
wind_data <- rbind(wind_sitesmatched_3,wind_sitesmatched_2,wind_sitesmatched_1)
# save(wind_data, file = "Data_P1/wind_data.RData")

# # RWS: You should never be removing values by specific call like this
#   # Rather you should be able to use some sort of conditional to screen out unwanted values
# wind_sitesmatched_1 <- wind_sitesmatched_1[-c(121352, 121353, 379892, 379893, 609324, 609325, 843506, 843507, 1014585), ]
# renaming_sites_2 <- function(df) {
#   sites <- df %>%
#     mutate(temp_sites = ifelse(station_name %in% c("ROBBENEILAND"), "Koeberg Basin",        
#                            ifelse(station_name %in% c("GEELBEK"), "Yzerfontein",
#                                 ifelse(station_name %in% c("DASSEN ISLAND"), "Dassen Island",
#                                        ifelse(station_name %in% c("ATLANTIS"), "Koeberg Basin","Error")))))
#   return(sites)
# }
# 
# wind_sitesmatched_2 <-  renaming_sites_2(df = wind_2)
# wind_sitesmatched_2 <- wind_sitesmatched_2[-c(228372, 228373, 313441, 313442, 364881, 364882, 557392), ] 
# renaming_sites_3 <- function(df) {
#   sites <- df %>%
#     mutate(temp_sites = ifelse(station_name %in% c("CAPE TOWN SLANGKOP"), "Kommetjie",  
#                            ifelse(station_name %in% c("CAPE TOWN - ROYAL YACHT CLUB"), "Sea Point",
#                            ifelse(station_name %in% c("CAPE TOWN TABLE BAY"), "Sea Point","Error"))))
#   return(sites)
# }
# 
# wind_sitesmatched_3 <-  renaming_sites_3(df = wind_3)
# wind_sitesmatched_3 <- wind_sitesmatched_3[-c(119317, 119318, 196551, 196552, 346759), ] 
### CAPE TOWN SLANGKOP may be used for Kommetjie and for Houtbay
# wind_3_HoutBay <- wind_3 %>% 
#   filter(station_name == "CAPE TOWN SLANGKOP") %>% 
#   mutate(temp_sites = ifelse(station_name %in% c("CAPE TOWN SLANGKOP"), "Hout Bay","Error"))
# wind_data <- rbind(wind_3_HoutBay,wind_sitesmatched_3,wind_sitesmatched_2,wind_sitesmatched_1)
# wind_data <- wind_data %>% 
#   na.omit()
# 
# wind_data <- wind_data %>% 
#   # mutate(date = as.Date(date)) %>%  
#   group_by(date, hour, temp_sites) 
# 
# # write.csv(wind_data, file = "Data_P1/wind_data.csv", row.names = T)
# # save(wind_data, file = "Data_P1/wind_data.RData")

@@

# wind_data <- read_csv("Data_P1/wind_data.csv")
selected_sites <- c("Port Nolloth", "Lamberts Bay", "Sea Point", "Saldanha Bay", "Yzerfontein", "Kommetjie")

wind_daily <- wind_data %>%
  # ungroup() %>%
  # mutate(date = as.Date(date))%>%
  dplyr::group_by(temp_sites, date) %>%
  filter(temp_sites %in% selected_sites) %>% 
  dplyr::summarise(dir_circ = round(mean.circular(circular(dir, units = "degrees")),2),
                   mean_speed = round(mean(speed),2))

# save(wind_daily, file = "Data_P1/wind_daily.RData")
# # Loading in the daily wind data

# Loading the subsetted wind data created from the text files above 
load("Data_P1/wind_daily.RData") 
```

@@

```{r}
load("Data_P1/SACTN_overlap.RData")
load("Data_P1/wind_daily.RData")
wind_daily <- wind_daily%>% 
  dplyr::rename(site = temp_sites) # Renaming to match the `match_func` previously created

insitu_wind <- match_func(df = wind_daily)  # Using `match_func`

insitu_wind <- insitu_wind %>% 
  filter(year(date) %in% seq(2010, 2014)) # The years 2010-2014 is the years of interest and the years for which wavelets are/will be created.

# save(insitu_wind, file = "Data_P1/insitu_wind.RData")
```

@@

```{r}
# Loading in the matched wind data
load("Data_P1/insitu_wind.RData")

wave_daily_renamed <- insitu_wind %>% 
  dplyr::rename(spd = mean_speed) %>%
  dplyr::rename(dir = dir_circ) 
source("functions/wind.rose.R")
p.wr2 <- plot.windrose(data = wave_daily_renamed,
              spd = "spd",
              dir = "dir")
p.wr3 <- p.wr2 + facet_wrap(.~ site, ncol = 2, nrow = "") +
  theme(strip.text.x = element_text(size = 25))
p.wr3 # RWS: You'll want to remove the NA part in the figure output
```

@@

# region <- "BC" # Benguela Current
# 
# coords <- c(-35, -20, 10, 20) # this is the BC
# 
# ncList <- list.files(path = MODIS_chlor.dir, pattern = "*.nc", full.names = TRUE, include.dirs = TRUE)
# strt.date <- str_sub(basename(ncList[1]), start = 2, end = 8)
# end.date <- str_sub(basename(ncList[length(ncList)]), start = 2, end = 8)
# nc.init <- nc_open(ncList[1])
# LatIdx <- which(nc.init$dim$lat$vals > coords[1] & nc.init$dim$lat$vals < coords[2])
# LonIdx <- which(nc.init$dim$lon$vals > coords[3] & nc.init$dim$lon$vals < coords[4])
# nc_close(nc.init)
# 
# 
# ncFun <- function(nc.file = nc.files, csv.dir = csv.dir) {
# nc <- nc_open(nc.file)
#   instrument <- ncatt_get(nc, 0, "instrument")$value
#   platform <- ncatt_get(nc, 0, "platform")$value
#   product_name <- ncatt_get(nc, 0, "product_name")$value
#   fNameStem <- substr(product_name, 17, 38)
#   timeStamp <- substr(product_name, 2, 8)
#   origin <- paste0(substr(timeStamp, 1, 4), "-01-01")
#   date <- as.Date(as.numeric(substr(timeStamp, 5, 7)), origin)
#   chl <- round(ncvar_get(nc,
#                    varid = "chlor_a",
#                    start = c(LonIdx[1], LatIdx[1]),
#                    count = c(length(LonIdx), length(LatIdx))),
#                3)
#   dimnames(chl) <- list(lon = nc$dim$lon$vals[LonIdx],
#                         lat =  nc$dim$lat$vals[LatIdx])
#   nc_close(nc)
#   chl <-
#     as.data.table(melt(chl, value.name = "chl"), row.names = NULL) %>%
#     mutate(t = date) %>%
#     na.omit()
#   fwrite(chl,
#          file = paste(csv.dir, "/", region, "-", instrument, ".",platform, ".",
#                       fNameStem, "-", strt.date, "-", end.date, ".csv", sep = ""),
#          append = TRUE, col.names = FALSE)
#   rm(chl)
# }
# 
# llply(ncList, ncFun, csv.dir = MODIS_chlor.csv.dir, .parallel = TRUE)

@@

# Loading the data
# load("Data_P1/MODIS_Chloro.RData") # Extracted/Raw chlorophyll data
# load("Data_P1/site_list_sub.Rdata") # Site list of all the sites along the west coast
# 
# # Visualisation
# chloro_plot <- MODIS_Chloro %>%
#   filter(date == min(date)) %>%
#   ggplot(aes(x = lon, y = lat)) +
#   geom_raster(aes(fill = chloro))
# 
# unique_pixel <- MODIS_Chloro %>% 
#   select(lon, lat) %>% 
#   unique()
# 
# match_index <- knnx.index(data = as.matrix(unique_pixel[,1:2]),
#                           query = as.matrix(site_list_sub[,5:6]), k = 1)
# 
# # Matching the chlorophylla-a lats and lons to the study sites
# pixel_match <- unique_pixel[match_index,] %>%
#   unite(col = combi, lon, lat, sep = "/", remove = F) %>%
#   mutate(site = site_list_sub$site)
# 
# chloro_match <- MODIS_Chloro %>%
#   unite(col = combi, lon, lat, sep = "/", remove = F) %>%
#   filter(combi %in% pixel_match$combi)
# 
# chloro_match %>%
#   filter(date == max(date)) %>%
#   ggplot(aes(x = lon, y = lat)) +
#   geom_raster(aes(fill = chloro))
# 
# chloro_sites <- chloro_match %>%
#   left_join(pixel_match, by = c("combi", "lon", "lat")) %>% 
#   dplyr::mutate(date = as.Date(date))
# # save(chloro_sites, file = "Data_P1/chloro_sites.RData")
# 
# # Visualisation
# load("Data_P1/chloro_sites.RData")
# Chloro_plot_complete <- ggplot(chloro_sites, aes(x = date, y = chloro)) +
#   geom_line() +
#   facet_wrap(~site, ncol = 1)
# Chloro_plot_complete
# 
# # Study period from 2010 - 2014
# chloro_data <- chloro_sites %>% 
#   filter(year(date) %in% seq(2010, 2014))
# # save(chloro_data, file = "Data_P1/chloro_data.RData")
# 
# # Plotting only years 2014-2015
# load("Data_P1/chloro_data.RData")
# Chloro_plot_filtered <- ggplot(chloro_data, aes(x = date, y = chloro)) +
#   geom_line() +
#   facet_wrap(~site, ncol = 1)
# Chloro_plot_filtered

@@

PCA_1 <- rda(tester)
summary(PCA)

# Proportion of variation explained
# Values to be found opon running the code

PCA <- cbind(scores(PCA_1, choices = c(1:4), display = "sites"))
PCA_spe <- cbind(scores(PCA_1, choices = c(1:4), display = "species"))

test1 <- ggplot(PCA, aes(x = lon, y = lat)) +
  geom_raster(aes(fill = PC1)) +
  geom_polygon(data = PC1, aes(long, lat, group = group),
               fill = NA, colour = "blue", size = 0.3) +
  geom_polygon(data = velocity, aes(long, lat, group = group),
               fill = NA, colour = "green", size = 0.3)+ 
         fill = guide_colourbar(title = "PC1")

test2 <- ggplot(PCA, aes(x = lon, y = lat)) +
  geom_raster(aes(fill = PC2)) +
  geom_polygon(data = PC1, aes(long, lat, group = group),
               fill = NA, colour = "blue", size = 0.3) +
  geom_polygon(data = velocity, aes(long, lat, group = group),
               fill = NA, colour = "green", size = 0.3)+ 
         fill = guide_colourbar(title = "PC2")
